Predicting the effects of character displacement on food-web dynamics

### 2019-02-09 manuscript_ECD_model.Rmd
fixed an important error in previous asymmetric sims. Now a_ii and a_ij are matched up properly.

## Linear
sim_2C_2R_MacArthur_linear <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_linear, 
                                init_states = states_2C_2R, 
                                eco_CR_model = MacArthur_2C_2R, 
                                AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_MacArthur_linear <- eco_evo_CR(init_parameters = params_1C_2R_MacArthur_linear, 
                                init_states = states_1C_2R, 
                                eco_CR_model = MacArthur_1C_2R, 
                                AD_CR_models = c(mC1_MacArthur),
                                species_traits = c(1), 
                                eco_param_names = c("a11"), 
                                eco_tradeoff_names = c("a12"),  
                                evo_param_names = c("a11m"),  
                                evo_tradeoff_names = c("a12m"), 
                                tradeoff_functions = c(a12_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))
# asymmetric starting points
params_2C_2R_MacArthur_linear_asymm <- params_2C_2R_MacArthur_linear
params_2C_2R_MacArthur_linear_asymm[c("a21","a22")] <- sim_1C_2R_MacArthur_linear[nrow(sim_1C_2R_MacArthur_linear), c("a11","a12")] # replace C2's attack rates with the ending point of the C1 generalist simulation. This will create an asymmetry in the attack rates and follows the logic (and our results) that a likely scenerio with asymmetry is a specialist invading a generalist.
# just altering the parameters, everything else stays the same
sim_2C_2R_MacArthur_linear_asymm <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_linear_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = MacArthur_2C_2R, 
                                AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))

## concaveDN
sim_2C_2R_MacArthur_concaveDN <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_concaveDN, 
                                init_states = states_2C_2R, 
                                eco_CR_model = MacArthur_2C_2R, 
                                AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))
sim_1C_2R_MacArthur_concaveDN <- eco_evo_CR(init_parameters = params_1C_2R_MacArthur_concaveDN, 
                                init_states = states_1C_2R, 
                                eco_CR_model = MacArthur_1C_2R, 
                                AD_CR_models = c(mC1_MacArthur),
                                species_traits = c(1), 
                                eco_param_names = c("a11"), 
                                eco_tradeoff_names = c("a12"),  
                                evo_param_names = c("a11m"),  
                                evo_tradeoff_names = c("a12m"), 
                                tradeoff_functions = c(a12_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))
# asymmetric starting points
params_2C_2R_MacArthur_concaveDN_asymm <- params_2C_2R_MacArthur_concaveDN
params_2C_2R_MacArthur_concaveDN_asymm[c("a21","a22")] <- sim_1C_2R_MacArthur_concaveDN[nrow(sim_1C_2R_MacArthur_concaveDN), c("a11","a12")] # replace C2's attack rates with the ending point of the C1 generalist simulation. This will create an asymmetry in the attack rates and follows the logic (and our results) that a likely scenerio with asymmetry is a specialist invading a generalist.
# just altering the parameters, everything else stays the same
sim_2C_2R_MacArthur_concaveDN_asymm <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_concaveDN_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = MacArthur_2C_2R, 
                                AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))

## concaveUP
sim_2C_2R_MacArthur_concaveUP <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_concaveUP, 
                                       init_states = states_2C_2R, 
                                       eco_CR_model = MacArthur_2C_2R, 
                                       AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                       species_traits = c(1,2), 
                                       eco_param_names = c("a11","a22"), 
                                       eco_tradeoff_names = c("a12","a21"),  
                                       evo_param_names = c("a11m","a22m"),  
                                       evo_tradeoff_names = c("a12m","a21m"), 
                                       tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveUP))
sim_1C_2R_MacArthur_concaveUP <- eco_evo_CR(init_parameters = params_1C_2R_MacArthur_concaveUP, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = MacArthur_1C_2R, 
                                       AD_CR_models = c(mC1_MacArthur),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveUP))
# asymmetric starting points
params_2C_2R_MacArthur_concaveUP_asymm <- params_2C_2R_MacArthur_concaveUP
params_2C_2R_MacArthur_concaveUP_asymm[c("a21","a22")] <- sim_1C_2R_MacArthur_concaveUP[nrow(sim_1C_2R_MacArthur_concaveUP), c("a11","a12")] # replace C2's attack rates with the ending point of the C1 generalist simulation. This will create an asymmetry in the attack rates and follows the logic (and our results) that a likely scenerio with asymmetry is a specialist invading a generalist.
# just altering the parameters, everything else stays the same

@@

## Linear
sim_2C_2R_LawlorSmith_linear <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_linear, 
                                       init_states = states_2C_2R, 
                                       eco_CR_model = LawlorSmith_2C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                       species_traits = c(1,2), 
                                       eco_param_names = c("a11","a22"), 
                                       eco_tradeoff_names = c("a12","a21"),  
                                       evo_param_names = c("a11m","a22m"),  
                                       evo_tradeoff_names = c("a12m","a21m"), 
                                       tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_LawlorSmith_linear <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_linear, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = LawlorSmith_1C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_linear))
# asymmetric starting points
params_2C_2R_LawlorSmith_linear_asymm <- params_2C_2R_LawlorSmith_linear
params_2C_2R_LawlorSmith_linear_asymm[c("a21","a22")] <- sim_1C_2R_LawlorSmith_linear[nrow(sim_1C_2R_LawlorSmith_linear), c("a11","a12")] 
sim_2C_2R_LawlorSmith_linear_asymm <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_linear_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = LawlorSmith_2C_2R, 
                                AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))

@@

sim_1C_2R_LawlorSmith_concaveDN <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_concaveDN, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = LawlorSmith_1C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveDN))
# asymmetric starting points
params_2C_2R_LawlorSmith_concaveDN_asymm <- params_2C_2R_LawlorSmith_concaveDN
params_2C_2R_LawlorSmith_concaveDN_asymm[c("a21","a22")] <- sim_1C_2R_LawlorSmith_concaveDN[nrow(sim_1C_2R_LawlorSmith_concaveDN), c("a11","a12")] 
sim_2C_2R_LawlorSmith_concaveDN_asymm <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveDN_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = LawlorSmith_2C_2R, 
                                AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))

## concaveUP
sim_2C_2R_LawlorSmith_concaveUP <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveUP, 
                                        init_states = states_2C_2R, 
                                        eco_CR_model = LawlorSmith_2C_2R, 
                                        AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                        species_traits = c(1,2), 
                                        eco_param_names = c("a11","a22"), 
                                        eco_tradeoff_names = c("a12","a21"),  
                                        evo_param_names = c("a11m","a22m"),  
                                        evo_tradeoff_names = c("a12m","a21m"), 
                                        tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                        extra_tradeoff_params = c(A=A, n=n_concaveUP))
sim_1C_2R_LawlorSmith_concaveUP <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_concaveUP, 
                                        init_states = states_1C_2R, 
                                        eco_CR_model = LawlorSmith_1C_2R, 
                                        AD_CR_models = c(mC1_LawlorSmith),
                                        species_traits = c(1), 
                                        eco_param_names = c("a11"), 
                                        eco_tradeoff_names = c("a12"),  
                                        evo_param_names = c("a11m"),  
                                        evo_tradeoff_names = c("a12m"), 
                                        tradeoff_functions = c(a12_tradeoff),
                                        extra_tradeoff_params = c(A=A, n=n_concaveUP))
# asymmetric starting points
params_2C_2R_LawlorSmith_concaveUP_asymm <- params_2C_2R_LawlorSmith_concaveUP
params_2C_2R_LawlorSmith_concaveUP_asymm[c("a21","a22")] <- sim_1C_2R_LawlorSmith_concaveUP[nrow(sim_1C_2R_LawlorSmith_concaveUP), c("a11","a12")] 
sim_2C_2R_LawlorSmith_concaveUP_asymm <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveUP_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = LawlorSmith_2C_2R, 
                                AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveUP))

@@

## Linear
sim_2C_2R_McCann_linear <- eco_evo_CR(init_parameters = params_2C_2R_McCann_linear, 
                                         init_states = states_2C_2R, 
                                         eco_CR_model = McCann_2C_2R, 
                                         AD_CR_models = c(mC1_McCann, mC2_McCann),
                                         species_traits = c(1,2), 
                                         eco_param_names = c("a11","a22"), 
                                         eco_tradeoff_names = c("a12","a21"),  
                                         evo_param_names = c("a11m","a22m"),  
                                         evo_tradeoff_names = c("a12m","a21m"), 
                                         tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_McCann_linear <- eco_evo_CR(init_parameters = params_1C_2R_McCann_linear, 
                                         init_states = states_1C_2R, 
                                         eco_CR_model = McCann_1C_2R, 
                                         AD_CR_models = c(mC1_McCann),
                                         species_traits = c(1), 
                                         eco_param_names = c("a11"), 
                                         eco_tradeoff_names = c("a12"),  
                                         evo_param_names = c("a11m"),  
                                         evo_tradeoff_names = c("a12m"), 
                                         tradeoff_functions = c(a12_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_linear))
# asymmetric starting points
params_2C_2R_McCann_linear_asymm <- params_2C_2R_McCann_linear
params_2C_2R_McCann_linear_asymm[c("a21","a22")] <- sim_1C_2R_McCann_linear[nrow(sim_1C_2R_McCann_linear), c("a11","a12")] 
sim_2C_2R_McCann_linear_asymm <- eco_evo_CR(init_parameters = params_2C_2R_McCann_linear_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = McCann_2C_2R, 
                                AD_CR_models = c(mC1_McCann, mC2_McCann),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))

# asymmetry with C1 starting with a different habitat preference (w)
params_1C_2R_McCann_linear_alt_w <- params_1C_2R_McCann_linear # NEED TO FIGURE OUT WHAT TO DO. i SHOULD PROBABLY MAKE SURE ATTACK RATES AND PREFERENCE ARE ALIGNED, BUT I SHOULD JUST DO THAT FOR THE ALTERNATIVE RESOURCE. E.G. C1 SPECIALIZING ON R2 INSTEAD OF R1 IN THE C1 ONLY SIMS.
sim_1C_2R_McCann_linear <- eco_evo_CR(init_parameters = params_1C_2R_McCann_linear_alt_w, 
                                         init_states = states_1C_2R, 
                                         eco_CR_model = McCann_1C_2R, 
                                         AD_CR_models = c(mC1_McCann),
                                         species_traits = c(1), 
                                         eco_param_names = c("a11"), 
                                         eco_tradeoff_names = c("a12"),  
                                         evo_param_names = c("a11m"),  
                                         evo_tradeoff_names = c("a12m"), 
                                         tradeoff_functions = c(a12_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_linear))

>>>>

## Linear
sim_2C_2R_MacArthur_linear <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_linear, 
                                init_states = states_2C_2R, 
                                eco_CR_model = MacArthur_2C_2R, 
                                AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_MacArthur_linear <- eco_evo_CR(init_parameters = params_1C_2R_MacArthur_linear, 
                                init_states = states_1C_2R, 
                                eco_CR_model = MacArthur_1C_2R, 
                                AD_CR_models = c(mC1_MacArthur),
                                species_traits = c(1), 
                                eco_param_names = c("a11"), 
                                eco_tradeoff_names = c("a12"),  
                                evo_param_names = c("a11m"),  
                                evo_tradeoff_names = c("a12m"), 
                                tradeoff_functions = c(a12_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))
# asymmetric starting points
params_2C_2R_MacArthur_linear_asymm <- params_2C_2R_MacArthur_linear
params_2C_2R_MacArthur_linear_asymm[c("a21","a22")] <- sim_1C_2R_MacArthur_linear[nrow(sim_1C_2R_MacArthur_linear), c("a12","a11")] # replace C2's attack rates with the ending point of the C1 generalist simulation. This will create an asymmetry in the attack rates and follows the logic (and our results) that a likely scenerio with asymmetry is a specialist invading a generalist.
# just altering the parameters, everything else stays the same
sim_2C_2R_MacArthur_linear_asymm <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_linear_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = MacArthur_2C_2R, 
                                AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))

## concaveDN
sim_2C_2R_MacArthur_concaveDN <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_concaveDN, 
                                init_states = states_2C_2R, 
                                eco_CR_model = MacArthur_2C_2R, 
                                AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))
sim_1C_2R_MacArthur_concaveDN <- eco_evo_CR(init_parameters = params_1C_2R_MacArthur_concaveDN, 
                                init_states = states_1C_2R, 
                                eco_CR_model = MacArthur_1C_2R, 
                                AD_CR_models = c(mC1_MacArthur),
                                species_traits = c(1), 
                                eco_param_names = c("a11"), 
                                eco_tradeoff_names = c("a12"),  
                                evo_param_names = c("a11m"),  
                                evo_tradeoff_names = c("a12m"), 
                                tradeoff_functions = c(a12_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))
# asymmetric starting points
params_2C_2R_MacArthur_concaveDN_asymm <- params_2C_2R_MacArthur_concaveDN
params_2C_2R_MacArthur_concaveDN_asymm[c("a21","a22")] <- sim_1C_2R_MacArthur_concaveDN[nrow(sim_1C_2R_MacArthur_concaveDN), c("a12","a11")] # replace C2's attack rates with the ending point of the C1 generalist simulation. This will create an asymmetry in the attack rates and follows the logic (and our results) that a likely scenerio with asymmetry is a specialist invading a generalist.
# just altering the parameters, everything else stays the same
sim_2C_2R_MacArthur_concaveDN_asymm <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_concaveDN_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = MacArthur_2C_2R, 
                                AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))

## concaveUP
sim_2C_2R_MacArthur_concaveUP <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_concaveUP, 
                                       init_states = states_2C_2R, 
                                       eco_CR_model = MacArthur_2C_2R, 
                                       AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                       species_traits = c(1,2), 
                                       eco_param_names = c("a11","a22"), 
                                       eco_tradeoff_names = c("a12","a21"),  
                                       evo_param_names = c("a11m","a22m"),  
                                       evo_tradeoff_names = c("a12m","a21m"), 
                                       tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveUP))
sim_1C_2R_MacArthur_concaveUP <- eco_evo_CR(init_parameters = params_1C_2R_MacArthur_concaveUP, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = MacArthur_1C_2R, 
                                       AD_CR_models = c(mC1_MacArthur),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveUP))
# asymmetric starting points
params_2C_2R_MacArthur_concaveUP_asymm <- params_2C_2R_MacArthur_concaveUP
params_2C_2R_MacArthur_concaveUP_asymm[c("a21","a22")] <- sim_1C_2R_MacArthur_concaveUP[nrow(sim_1C_2R_MacArthur_concaveUP), c("a12","a11")] # replace C2's attack rates with the ending point of the C1 generalist simulation. This will create an asymmetry in the attack rates and follows the logic (and our results) that a likely scenerio with asymmetry is a specialist invading a generalist.
# just altering the parameters, everything else stays the same

@@

## Linear
sim_2C_2R_LawlorSmith_linear <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_linear, 
                                       init_states = states_2C_2R, 
                                       eco_CR_model = LawlorSmith_2C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                       species_traits = c(1,2), 
                                       eco_param_names = c("a11","a22"), 
                                       eco_tradeoff_names = c("a12","a21"),  
                                       evo_param_names = c("a11m","a22m"),  
                                       evo_tradeoff_names = c("a12m","a21m"), 
                                       tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_LawlorSmith_linear <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_linear, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = LawlorSmith_1C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_linear))
# asymmetric starting points
params_2C_2R_LawlorSmith_linear_asymm <- params_2C_2R_LawlorSmith_linear
params_2C_2R_LawlorSmith_linear_asymm[c("a21","a22")] <- sim_1C_2R_LawlorSmith_linear[nrow(sim_1C_2R_LawlorSmith_linear), c("a12","a11")] 
sim_2C_2R_LawlorSmith_linear_asymm <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_linear_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = LawlorSmith_2C_2R, 
                                AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))

@@

sim_1C_2R_LawlorSmith_concaveDN <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_concaveDN, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = LawlorSmith_1C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveDN))
# asymmetric starting points
params_2C_2R_LawlorSmith_concaveDN_asymm <- params_2C_2R_LawlorSmith_concaveDN
params_2C_2R_LawlorSmith_concaveDN_asymm[c("a21","a22")] <- sim_1C_2R_LawlorSmith_concaveDN[nrow(sim_1C_2R_LawlorSmith_concaveDN), c("a12","a11")] 
sim_2C_2R_LawlorSmith_concaveDN_asymm <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveDN_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = LawlorSmith_2C_2R, 
                                AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))

## concaveUP
sim_2C_2R_LawlorSmith_concaveUP <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveUP, 
                                        init_states = states_2C_2R, 
                                        eco_CR_model = LawlorSmith_2C_2R, 
                                        AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                        species_traits = c(1,2), 
                                        eco_param_names = c("a11","a22"), 
                                        eco_tradeoff_names = c("a12","a21"),  
                                        evo_param_names = c("a11m","a22m"),  
                                        evo_tradeoff_names = c("a12m","a21m"), 
                                        tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                        extra_tradeoff_params = c(A=A, n=n_concaveUP))
sim_1C_2R_LawlorSmith_concaveUP <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_concaveUP, 
                                        init_states = states_1C_2R, 
                                        eco_CR_model = LawlorSmith_1C_2R, 
                                        AD_CR_models = c(mC1_LawlorSmith),
                                        species_traits = c(1), 
                                        eco_param_names = c("a11"), 
                                        eco_tradeoff_names = c("a12"),  
                                        evo_param_names = c("a11m"),  
                                        evo_tradeoff_names = c("a12m"), 
                                        tradeoff_functions = c(a12_tradeoff),
                                        extra_tradeoff_params = c(A=A, n=n_concaveUP))
# asymmetric starting points
params_2C_2R_LawlorSmith_concaveUP_asymm <- params_2C_2R_LawlorSmith_concaveUP
params_2C_2R_LawlorSmith_concaveUP_asymm[c("a21","a22")] <- sim_1C_2R_LawlorSmith_concaveUP[nrow(sim_1C_2R_LawlorSmith_concaveUP), c("a12","a11")] 
sim_2C_2R_LawlorSmith_concaveUP_asymm <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveUP_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = LawlorSmith_2C_2R, 
                                AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveUP))

@@

## Linear
sim_2C_2R_McCann_linear <- eco_evo_CR(init_parameters = params_2C_2R_McCann_linear, 
                                         init_states = states_2C_2R, 
                                         eco_CR_model = McCann_2C_2R, 
                                         AD_CR_models = c(mC1_McCann, mC2_McCann),
                                         species_traits = c(1,2), 
                                         eco_param_names = c("a11","a22"), 
                                         eco_tradeoff_names = c("a12","a21"),  
                                         evo_param_names = c("a11m","a22m"),  
                                         evo_tradeoff_names = c("a12m","a21m"), 
                                         tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_McCann_linear <- eco_evo_CR(init_parameters = params_1C_2R_McCann_linear, 
                                         init_states = states_1C_2R, 
                                         eco_CR_model = McCann_1C_2R, 
                                         AD_CR_models = c(mC1_McCann),
                                         species_traits = c(1), 
                                         eco_param_names = c("a11"), 
                                         eco_tradeoff_names = c("a12"),  
                                         evo_param_names = c("a11m"),  
                                         evo_tradeoff_names = c("a12m"), 
                                         tradeoff_functions = c(a12_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_linear))
# I'm thinking these initial asymmetric simulations don't quite make sense (at least for LawlorSmith and McCann). This is because I didn't switch the pre-adapted habitat preferences as well...This is important because C1 in the first simulation becomes C2 in the 2C-2R sim. This isn't an issue in the symmetry model, because I assume they are pre-adapted on different resources. 
# asymmetric starting points
params_2C_2R_McCann_linear_asymm <- params_2C_2R_McCann_linear
params_2C_2R_McCann_linear_asymm[c("a21","a22")] <- sim_1C_2R_McCann_linear[nrow(sim_1C_2R_McCann_linear), c("a12","a11")] # make sure a_ij and a_ii are in correct order. Note that habitat preference (w) is already set in the appropriate direction 
sim_2C_2R_McCann_linear_asymm <- eco_evo_CR(init_parameters = params_2C_2R_McCann_linear_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = McCann_2C_2R, 
                                AD_CR_models = c(mC1_McCann, mC2_McCann),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))
